---
title: "NityaSruti"
author: "Kanekalla"
date: "September 8, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Regular Expression

grep : Returns index of the object where a regular expression was found in the string
```{r }
x<-c("HSPA1A","HSPA1B","HSPA1L","HSPA4","HSPA4L")
grep("HSPA4",x) 
```
grepl : Returns logical values for regular expression matching 
to get the match that has either "HSPA1A" or "HSPA1B" in a the string names
```{r }
grepl( "HSPA1A|B",x)
```
##sub : Substitute a pattern with a given string at first occurrence only

```{r}
y<-"These genes are HSP70 genes"
sub("genes", "------GEEEEEENEEES----",y )           
     
```
##gsub: Substitute a pattern with a given string globally/all occurances
```{r}
gsub("genes", "------GEEEEEENEEES----",y )    
```

regexpr : Return the first position of found string by regular expression
gregexpr : Return all positions of test string by regular expression
```{r}
regexpr("SPA1",x ) 
gregexpr("SPA1",x)
```

substr: Extract or replace substrings in a character vector
```{r}
#y 
substr(y, 7,11)

```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
